---
name: "`r params$header$name`"
position: "\\Large `r params$highlight$job_title`"
address: | 
         |
         | `r if (!is.na(params$header$address_line)) params$header$address_line`
profilepic: "`r params$header$profilpic`"
phone: "`r if (!is.na(params$header$phone)) as.character(params$header$phone)`"
email: "`r as.character(params$header$email)`"
github: "`r if (!is.na(params$header$github)) params$header$github`"
linkedin: "`r if (!is.na(params$header$linkedin)) params$header$linkedin`"
www: "`r if (!is.na(params$header$www)) params$header$www`"
headcolor: "`r params$highlight$color`"
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    keep_tex: false
    show_footer: true
    includes:
      in_header: header.txt
params:
  header: NULL
  data: NULL
  highlight: NULL
always_allow_html: yes
editor_options: 
  chunk_output_type: console
---

<!-- DON'T TOUCH ANYTHING ABOVE THIS LINE UNLESS YOU KNOW WHAT YOU'RE DOING -->

```{r setup, include=FALSE}
## DO NOT TOUCH THIS UNLESS YOU KNOW WHAT YOU'RE DOING
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(dplyr)
#library(ggrepel)
library(emojifont)
library(fontawesome)
library(kableExtra)
#library(huxtable)
#library(gridExtra)
library(magrittr)

replace_ampersand <- function(df) {
  # Apply gsub function to replace "&" with "\&" in all character columns
  df[] <- lapply(df, function(x) {
    if(is.character(x)) {
      x <- iconv(x, to = "UTF-8", sub = "")
      gsub("&", "\\&", x, fixed = TRUE)
    } else {
      x
    }
  })
  return(df)
}

```

\

<!-- YOU CAN CHANGE OR TRANSLATE THE PART "Why I'm the right fit for" IF YOU LIKE -->
<!-- IF YOU WANT TO DELETE THIS SECTION, DELETE EVERYTHING UNTIL THE NEXT GREEN TEXT LINE -->
\faIcon{check-circle} `r params$highlight$hl_title`
============================================

```{r color-definition, results='asis', echo=FALSE}
cat(paste0("\\definecolor{customcolor}{HTML}{", params$highlight$color, "}"))
```
\begin{multicols}{3}
\begin{tcolorbox}[colback=customcolor!50, colframe=customcolor!50, coltext=white, size=small]
    \begin{center}
        `r params$highlight$highlight_1`
    \end{center}
\end{tcolorbox}

\begin{tcolorbox}[colback=customcolor!50, colframe=customcolor!50, coltext=white, size=small]
    \begin{center}
          `r params$highlight$highlight_2`
    \end{center}
\end{tcolorbox}

\begin{tcolorbox}[colback=customcolor!50, colframe=customcolor!50, coltext=white, size=small]
    \begin{center}
          `r params$highlight$highlight_3`
    \end{center}
\end{tcolorbox}
\end{multicols}


<!-- YOU CAN CHANGE OR TRANSLATE THE PART "Professional Experience" IF YOU LIKE -->
<!-- IF YOU WANT TO DELETE THIS SECTION, DELETE EVERYTHING UNTIL THE NEXT GREEN TEXT LINE -->
\faIcon{briefcase} Professional Experience
============================================


```{r work}
## DO NOT TOUCH THIS UNLESS YOU KNOW WHAT YOU'RE DOING
params$data$work %>% replace_ampersand() %>%
  detailed_entries(company, dates, position, loc, details, .protect=FALSE)

```


\newpage

<!-- YOU CAN CHANGE OR TRANSLATE THE PART "Education" IF YOU LIKE -->
<!-- IF YOU WANT TO DELETE THIS SECTION, DELETE EVERYTHING UNTIL THE NEXT GREEN TEXT LINE -->
\faIcon{university} Education
==================================


```{r education}
## DO NOT TOUCH THIS UNLESS YOU KNOW WHAT YOU'RE DOING
params$data$education %>% replace_ampersand() %>%
  detailed_entries(study, dates, university, loc, details, .protect=FALSE)

```


<!-- YOU CAN CHANGE OR TRANSLATE THE PART "Skills" IF YOU LIKE -->
<!-- IF YOU WANT TO DELETE THIS SECTION, DELETE EVERYTHING UNTIL THE NEXT GREEN TEXT LINE -->
\faIcon{brain} Skills
================================

```{r skills}
## DO NOT TOUCH THIS UNLESS YOU KNOW WHAT YOU'RE DOING
params$data$skills  %>% replace_ampersand() %>%
  detailed_entries(
    with = area,
    what = skill
  )

```



<!-- YOU CAN CHANGE OR TRANSLATE THE PART "Reference Projects & Media" IF YOU LIKE -->
<!-- IF YOU WANT TO DELETE THIS SECTION, DELETE EVERYTHING UNTIL THE NEXT GREEN TEXT LINE -->
\faIcon{laptop-code} Reference Projects & Media
================================

```{r projects}
## DO NOT TOUCH THIS UNLESS YOU KNOW WHAT YOU'RE DOING
params$data$projects  %>% replace_ampersand() %>%
  brief_entries(with = lang, what = sum, when = link, .protect=FALSE)

```


<!-- YOU CAN CHANGE OR TRANSLATE THE PART "Volunteer work " IF YOU LIKE -->
<!-- IF YOU WANT TO DELETE THIS SECTION, DELETE EVERYTHING UNTIL THE NEXT GREEN TEXT LINE -->
\faIcon{hand-holding-heart} Volunteer work 
================================

```{r vol}
## DO NOT TOUCH THIS UNLESS YOU KNOW WHAT YOU'RE DOING
params$data$volunteer  %>% replace_ampersand() %>%
  brief_entries(with = lang, what = sum, when = link, .protect=FALSE)

```


\
\
<!-- YOU CAN CHANGE OR TRANSLATE THE PART "For references and restimonials, please contact me." IF YOU LIKE -->
<!-- IF YOU WANT TO DELETE THIS SECTION, DELETE EVERYTHING -->
\textcolor{lightgray}{\textit{For references and testimonials, please contact me.}}


