
---
output:
  pdf_document:
    keep_tex: true
    latex_engine: xelatex
    includes:
      in_header: header_letter.tex
params:
  header: NULL
  text: NULL


---


<!-- <!-- DON'T TOUCH ANYTHING ABOVE THIS LINE UNLESS YOU KNOW WHAT YOU'RE DOING --> 

```{r setup, include=FALSE}
## DO NOT TOUCH THIS UNLESS YOU KNOW WHAT YOU'RE DOING
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# library(fontawesome)
# library(kableExtra)
#library(huxtable)
#library(gridExtra)
library(magrittr)
# \mytitle{Bewerbung als Kammerjäger}

```


\definecolor{mycolor}{HTML}{`r params$header$color`}
\helveticatext


\rhead{
  \centering
  \myname{\textcolor{mycolor}{`r params$header$name`}}
  \myaddress{ | }
  \myaddress{`r params$header$address`}
  \myaddress{ | }
  \myaddress{`r params$header$email`}
}

\fancyfoot[L]{\myfooter{\today}}
\fancyfoot[C]{\myfooter{`r params$header$footer`}}
\fancyfoot[R]{\myfooter{\thepage}}
\addtolength{\footskip}{-80pt}
\thispagestyle{fancy}


\begin{flushleft}
\textbf{`r params$text$company_address_1` \hfill \today} \\
`r params$text$company_address_2` 
`r params$text$company_address_3`
\end{flushleft}

\
\

\textcolor{mycolor}{`r params$text$letter_title`}
============================================

\

`r params$text$concern`,

`r params$text$intro`

`r params$text$main`

`r params$text$company`

`r params$text$final`


\

\begin{adjustwidth}{2em}{}

`r params$header$greeting_line`

`r params$header$name`


```{r, echo=FALSE, warning=FALSE, out.height='50pt', fig.align='left'}
img_path <- params$header$signature
if (file.exists(img_path)) {
  knitr::include_graphics(img_path)
}
```

\end{adjustwidth}